---
title: "Stat. 651 Homework 2"
author: " Stephanie Mojica"
output:
  html_document: default
  pdf_document: default
  word_document: default
date: "10-31-2022"
---

### Chapter 14

## Exercise 3

```{r}
library(pacman)
p_load(ggplot2, macleish, lubridate, zoo, plotly,shiny)

whately_2015$when <- as.Date(whately_2015$when)

yq <- as.yearqtr(as.yearmon(whately_2015$when, "%Y/%m/%d") + 1/12)
whately_2015$Season <- factor(format(yq, "%q"), levels = 1:4,
                labels = c("Winter Solstice", "Vernal Equinox", "Summer Solstice", "Autumnal Equinox"))
head(whately_2015)

whately_2015_plot <- ggplot(data = whately_2015, aes(x = when, y = temperature)) +
  geom_point(aes(color = Season), size = 2)
ggplotly(whately_2015_plot)



```



## Exercise 4

```{r, Data wrangling}
p_load(tidyverse, shiny, shinybusy,mdsr, DT)

mergedViolations <- Violations %>%
  left_join(Cuisines)

mergedViolations %>%
  select(dba,boro,cuisine_description) %>% 
  group_by(dba) %>%
  count(cuisine_description) %>%
  filter(cuisine_description == "Pizza")

mergedViolations %>%
  select(dba,boro,cuisine_description) %>% 
 filter(boro == "BROOKLYN") %>%
  group_by(dba) %>%
  count(cuisine_description) %>%
  filter(cuisine_description == "Caribbean")





ui <- fluidPage(
  titlePanel("Number of Restaurants in a Cuisine"),
  fluidRow(
    # some things take time: this lets users know
    add_busy_spinner(spin = "fading-circle"),
    column(
      4,
      selectInput(inputId = "boro",
                  label = "Borough:",
                  choices = c(
                    "ALL",
                    unique(as.character(mergedViolations$boro))
                  )
      )
    ),
    # display dynamic list of cuisines
    column(4, uiOutput("cuisinecontrols"))
  ),
  # Create a new row for the table.
  fluidRow(
    DT::dataTableOutput("table")
  )
)

server <- function(input, output) {
  datasetboro <- reactive({ # Filter data based on selections
    req(input$boro)
    data <- mergedViolations %>%
      select(dba,boro,cuisine_description) %>% 
    group_by(dba) %>%
    count(cuisine_description)

})
  
  datasetcuisine <- reactive({  # dynamic list of cuisines
    req(input$cuisine)   # wait until list is available
    data <- datasetboro() %>%
      unique()
    if (input$cuisine != "ALL") {
      data <- data %>%
        filter(cuisine_description == input$cuisine)
    }
    data
  })
  
  output$table <- DT::renderDataTable(DT::datatable(datasetcuisine()))
  
  output$cuisinecontrols <- renderUI({
    availablelevels <-
      unique(sort(as.character(datasetboro()$cuisine_description)))
    selectInput(
      inputId = "cuisine",
      label = "Cuisine:",
      choices = c("ALL", availablelevels)
    )
  })
}

shinyApp(ui = ui, server = server)
```


## Exercise 6

```{r}
p_load(ggExtra, nasaweather)

p <- ggplot(storms, aes(x = wind, y = pressure)) +
  geom_point() +
  theme_classic() +
  stat_smooth(method = "loess", formula = y ~ x, size = 2)
ggExtra::ggMarginal(p, type = "histogram", binwidth = 3)

```

This scatterplot shows a negative linear association between wind and pressure in Tropical cyclone tracks through the Atlantic Ocean, Caribbean Sea and Gulf of Mexico from 1995 to 2005, as the pressure increases, the wind decreases. The histograms also give us an insight between the relationship between the two variables. The pressure is higher in millibars when the wind is less than 40 knots. 


## Exercise 7


```{r}
library(shiny)

p_load(tidyverse, shiny, shinybusy,mdsr, DT, palmerpenguins)

penguins<- palmerpenguins::penguins




ui <- fluidPage(
  titlePanel("Palmer Penguins"),
  fluidRow(
    # some things take time: this lets users know
    add_busy_spinner(spin = "fading-circle"),
    column(
      4,
      selectInput(inputId = "species",
                  label = "Select Species:",
                  choices = c(
                    "ALL",
                    unique(as.character(penguins$species))
                  )
      )
    ),
    # display dynamic list of cuisines
    column(4, uiOutput("speciescontrols"))
  ),
  # Create a new row for the table.
  fluidRow(
    DT::dataTableOutput("table")
  )
)

server <- function(input, output) {
  datasetspecies <- reactive({ # Filter data based on selections
    req(input$species)
    data <- penguins %>%
      select(species,sex,island,bill_length_mm, bill_depth_mm,flipper_length_mm,body_mass_g, year ) %>%
      group_by(species)
      
    
  })
  
  datasetsex <- reactive({  # dynamic list of cuisines
    req(input$sex)   # wait until list is available
    data <- datasetspecies() %>%
      unique()
    if (input$sex != "ALL") {
      data <- data %>%
        filter(sex == input$sex)
    }
    data
  })
  
  output$table <- DT::renderDataTable(DT::datatable(datasetsex()))
  
  output$speciescontrols <- renderUI({
    availablelevels <-
      unique(sort(as.character(datasetspecies()$sex)))
    selectInput(
      inputId = "sex",
      label = "Select Gender:",
      choices = c("ALL", availablelevels)
    )
  })
}


shinyApp(ui = ui, server = server)
```



## Exercise 8

```{r}

p_load(macleish, dplyr)

whately<- macleish::whately_2015
orchard<- macleish::orchard_2015

ui <- fluidPage(
  titlePanel("Weather data"),
  fluidRow(
    # some things take time: this lets users know
    add_busy_spinner(spin = "fading-circle"),
    column(
      4,
      selectInput(inputId = "data",
                  label = "Select Data:",
                  choices = c(
                    "orchard", "whately"
                  
                  )
      )
    ),
    # display dynamic list of cuisines
    column(4, uiOutput("datacontrols"))
  ),
  # Create a new row for the table.
  fluidRow(
    DT::dataTableOutput("table")
  )
)

server <- function(input, output) {
  datasetweather <- reactive({ # Filter data based on selections
    req(input$data)
    data <- select(orchard, whately)
    
    
  })
  
  datasetwhen <- reactive({  # dynamic list of cuisines
    req(input$when)   # wait until list is available
    data <- datasetweather() %>%
      unique()
    if (input$when != "ALL") {
      data <- data %>%
        filter(when == input$when)
    }
    data
  })
  
  output$table <- DT::renderDataTable(DT::datatable(datasetwhen()))
  
  output$datacontrols <- renderUI({
    availablelevels <-
      unique(sort(as.character(datasetweather()$when)))
    selectInput(
      inputId = "when",
      label = "Select Date:",
      choices = c("ALL", availablelevels)
    )
  })
}

shinyApp(ui = ui, server = server)


```

